Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-21 awipev-CO2.Rmd
variable modification ; sal temp

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
```

@@

### **Sal FB / Sal *in situ* **
```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE}

@@

#Plot for philipp
sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
geom_point(aes(y=sal_fb,col="FB") , size=2) +
geom_point(aes(y=sal_insitu, col="in situ"))  +
labs(title=  "salinity 2015", x = "Time", y= "")

sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
geom_point(aes(y=sal_fb,col="FB") , size=2) +
geom_point(aes(y=sal_insitu, col="in situ"))  +
labs(title=  "salinity 2019", x = "Time", y= "")

ggsave("figures/sal_2019.png", sal_19, units="cm")
ggsave("figures/sal_2015.png", sal_15, units="cm")
ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  #dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb=sal_fb_filtered, sal_insitu_ctds=sal_insitu_ctds_filtered, temp_fb=temp_fb_filtered)
```

@@

### **Sal FB / Sal *in situ* **
```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
########### Binding sal_fb INTO sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu))

@@

# #Plot for philipp
# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
# geom_point(aes(y=sal_fb,col="FB") , size=2) +
# geom_point(aes(y=sal_insitu, col="in situ"))  +
# labs(title=  "salinity 2015", x = "Time", y= "")
# 
# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
# geom_point(aes(y=sal_fb,col="FB") , size=2) +
# geom_point(aes(y=sal_insitu, col="in situ"))  +
# labs(title=  "salinity 2019", x = "Time", y= "")
# 
# ggsave("figures/sal_2019.png", sal_19, units="cm")
# ggsave("figures/sal_2015.png", sal_15, units="cm")
# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")

@@

# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
 # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y",valueRange = c(-3, 9))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
